Predicting political party affiliation from text

### 2016-06-17 manuscript/poltext.tex
removed web app references, added authors

\author{Felix Biessmann\\
  {\tt felix.biessmann@gmail.com} \\ \And
  Sebastian Schelter\\
  Technische Universit\"at Berlin\\
  {\tt sebastian.schelter@tu-berlin.de}\\
  \And
 Pola Lehmann \\
  Wissenschaftszentrum Berlin \\
  {\tt pola.lehmann@wzb.eu} \\}

@@

\begin{abstract}
Every day large amounts of text are produced in public discourse. Some of this text is produced by actors whose political colour is very obvious, for example in the case of party elites. But there are also many actors raising their voices in the discourse, who cannot be clearly attributed to a political party, while their statements might actually by biased towards a specific party. Identifying such biases is crucial for political research as well as media consumers, especially when analysing the influence of the media on political discourse and vice versa. In this study we investigate to what extent political party affiliation can be predicted from textual content. Results indicate that automatic classification of political affiliation is possible with above chance accuracy also across text domains. We propose methods to better interpret these results and find that features not related to political policies, such as speech sentiment, can be discriminative and thus exploited by text analysis models. We present an example of a web application that combines topic modelling with automatic political affiliation analyses of news articles based on the proposed model.
\end{abstract}

>>>>

\author{Felix Biessmann\\
%  {\tt felix.biessmann@gmail.com} \\ 
  \And
  Sebastian Schelter\\
  Technische Universit\"at Berlin\\
%  {\tt sebastian.schelter@tu-berlin.de}\\
\And 
Daniel Kirsch
  \And
 Pola Lehmann \\
  Wissenschaftszentrum Berlin \\
%  {\tt pola.lehmann@wzb.eu} \\
  }

@@

\begin{abstract}
Every day large amounts of text are produced in public discourse. Some of this text is produced by actors whose political colour is very obvious, for example in the case of party elites. But there are also many actors raising their voices in the discourse, who cannot be clearly attributed to a political party, while their statements might actually by biased towards a specific party. Identifying such biases is crucial for political research as well as media consumers, especially when analysing the influence of the media on political discourse and vice versa. In this study we investigate to what extent political party affiliation can be predicted from textual content. Results indicate that automatic classification of political affiliation is possible with above chance accuracy also across text domains. We propose methods to better interpret these results and find that features not related to political policies, such as speech sentiment, can be discriminative and thus exploited by text analysis models. 
%We present an example of a web application that combines topic modelling with automatic political affiliation analyses of news articles based on the proposed model.
\end{abstract}
